---
title: "Vaccination Rates (FeFemales)"
author: "Tori Diamond"
date: '2022-06-23'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
library(magrittr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ggplot2)
library(patchwork)
library(ggnewscale)
```

## Creating weights for each population type
```{r}
## creating weights df
weights.df <- read_excel("Weights.xlsx", sheet = "HSU&ERP")

# HSU total weights
# using numbers
HSUn.df <- weights.df[-c(2:12), ]
HSUn.df <- pivot_longer(HSUn.df, cols = 3:20, names_to = "AgeGroup", values_to = "Weights") # changing from rows to column
HSUn.df <- HSUn.df[, c(3, 4)] # only showing weights by age-groups

# HSU Maori weights
# using numbers
HSUMn.df <- weights.df[-c(1:2, 4:12), ]
HSUMn.df <- pivot_longer(HSUMn.df, cols = 3:20, names_to = "AgeGroup", values_to = "Weights") # changing from rows to column
HSUMn.df <- HSUMn.df[, c(3, 4)] # only showing weights by age-groups

# HSU NonMaori weights
# using numbers
HSUNMn.df <- weights.df[-c(1:4, 6:12), ]
HSUNMn.df <- pivot_longer(HSUNMn.df, cols = 3:20, names_to = "AgeGroup", values_to = "Weights") # changing from rows to column
HSUNMn.df <- HSUNMn.df[, c(3, 4)] # only showing weights by age-groups


# ERP total weights
# using numbers
ERPn.df <- weights.df[-c(1:6, 8:12), ]
ERPn.df <- pivot_longer(ERPn.df, cols = 3:20, names_to = "AgeGroup", values_to = "Weights") # changing from rows to column
ERPn.df <- ERPn.df[, c(3, 4)] # only showing weights by age-groups

# ERP Maori weights
# using numbers
ERPMn.df <- weights.df[-c(1:8, 10:12), ]
ERPMn.df <- pivot_longer(ERPMn.df, cols = 3:20, names_to = "AgeGroup", values_to = "Weights") # changing from rows to column
ERPMn.df <- ERPMn.df[, c(3, 4)] # only showing weights by age-groups

# ERP NonMaori weights
# using numbers
ERPNMn.df <- weights.df[-c(1:10, 12), ]
ERPNMn.df <- pivot_longer(ERPNMn.df, cols = 3:20, names_to = "AgeGroup", values_to = "Weights") # changing from rows to column
ERPNMn.df <- ERPNMn.df[, c(3, 4)] # only showing weights by age-groups
```

## Total Fully Vaccinated Rates

```{r}
# Total fully vaccinated
TFVacc_SFnontotal.df <- read_excel("VaccinationDataR Updated HSU2021.xlsx", sheet = "TotalFullVacc")
TFVacc_SFnontotal.df <- subset(TFVacc_SFnontotal.df, Group != "Total" & Group != "Male" & DHB != "Total")

TFVacc_SFnontotal.df <- pivot_longer(TFVacc_SFnontotal.df, cols = 4:20, names_to = "AgeGroup", values_to = "Count") # changing from rows to column
TFVacc_SFnontotal.df <- TFVacc_SFnontotal.df[, c(1, 4, 5, 3)] # rearranging columns to match Daniel's example below


# Using HSU Weights

## Join on the standard population weights (adds in a column called "Weights")
HSU_TFVacc_SFnontot.df <- left_join(TFVacc_SFnontotal.df, HSUn.df, by = "AgeGroup")


## Create a dataset for the total of each DHB (all age groups summed), doesn't include all DHB named 'Total'
HSU_TFVacc_SFtot.df <- HSU_TFVacc_SFnontot.df %>%
  group_by(DHB) %>%
  summarise(
    AgeGroup = "Total",
    Count = sum(Count), Total = sum(Weights) # sum weights as want to divide by total HSU population for Rate
  )

## Calculate the age-specific rates for each age group in each year
alpha <- 0.05 # added this in for 95% CI
HSU_TFVacc_SFnontot.df <- HSU_TFVacc_SFnontot.df %>%
  mutate(
    Rate = Count / Weights, # dividing by age-band population for rate
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Weights^2

    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE)) * 100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance)) * 100000,
    Rate_Gamma1Lwr = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights) * 100000,
    Rate_Gamma1Upr = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights) * 100000
  )

# Using ERP Weights

## Join on the standard population weights (adds in a column called "Weights")
ERP_TFVacc_SFnontot.df <- left_join(TFVacc_SFnontotal.df, ERPn.df, by = "AgeGroup")


## Create a dataset for the total of each DHB (all age groups summed), doesn't include all DHB named 'Total'
ERP_TFVacc_SFtot.df <- ERP_TFVacc_SFnontot.df %>%
  group_by(DHB) %>%
  summarise(
    AgeGroup = "Total",
    Count = sum(Count), Total = sum(Weights) # sum weights as want to divide by total HSU population for Rate
  )

## Calculate the age-specific rates for each age group in each year
alpha <- 0.05 # added this in for 95% CI
ERP_TFVacc_SFnontot.df <- ERP_TFVacc_SFnontot.df %>%
  mutate(
    Rate = Count / Weights, # dividing by age-band population for rate
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Weights^2

    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE)) * 100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance)) * 100000,
    Rate_Gamma1Lwr = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights) * 100000,
    Rate_Gamma1Upr = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights) * 100000
  )
```


## M훮ori Fully Vaccinated Rates

```{r}
# Total fully vaccinated
MFVacc_SFnontotal.df <- read_excel("VaccinationDataR Updated HSU2021.xlsx", sheet = "MaoriFullVacc")
MFVacc_SFnontotal.df <- subset(MFVacc_SFnontotal.df, Group != "Total" & Group != "Male" & DHB != "Total")

MFVacc_SFnontotal.df <- pivot_longer(MFVacc_SFnontotal.df, cols = 4:20, names_to = "AgeGroup", values_to = "Count") # changing from rows to column
MFVacc_SFnontotal.df <- MFVacc_SFnontotal.df[, c(1, 4, 5, 3)] # rearranging columns to match Daniel's example below


# Using HSU Weights

## Join on the standard population weights (adds in a column called "Weights")
HSU_MFVacc_SFnontot.df <- left_join(MFVacc_SFnontotal.df, HSUMn.df, by = "AgeGroup")


## Create a dataset for the total of each DHB (all age groups summed), doesn't include all DHB named 'Total'
HSU_MFVacc_SFtot.df <- HSU_MFVacc_SFnontot.df %>%
  group_by(DHB) %>%
  summarise(
    AgeGroup = "Total",
    Count = sum(Count), Total = sum(Weights) # sum weights as want to divide by total HSU population for Rate
  )

## Calculate the age-specific rates for each age group in each year
alpha <- 0.05 # added this in for 95% CI
HSU_MFVacc_SFnontot.df <- HSU_MFVacc_SFnontot.df %>%
  mutate(
    Rate = Count / Weights, # dividing by age-band population for rate
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Weights^2

    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE)) * 100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance)) * 100000,
    Rate_Gamma1Lwr = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights) * 100000,
    Rate_Gamma1Upr = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights) * 100000
  )

# Using ERP Weights

## Join on the standard population weights (adds in a column called "Weights")
ERP_MFVacc_SFnontot.df <- left_join(MFVacc_SFnontotal.df, ERPMn.df, by = "AgeGroup")


## Create a dataset for the total of each DHB (all age groups summed), doesn't include all DHB named 'Total'
ERP_MFVacc_SFtot.df <- ERP_MFVacc_SFnontot.df %>%
  group_by(DHB) %>%
  summarise(
    AgeGroup = "Total",
    Count = sum(Count), Total = sum(Weights) # sum weights as want to divide by total HSU population for Rate
  )

## Calculate the age-specific rates for each age group in each year
alpha <- 0.05 # added this in for 95% CI
ERP_MFVacc_SFnontot.df <- ERP_MFVacc_SFnontot.df %>%
  mutate(
    Rate = Count / Weights, # dividing by age-band population for rate
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Weights^2

    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE)) * 100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance)) * 100000,
    Rate_Gamma1Lwr = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights) * 100000,
    Rate_Gamma1Upr = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights) * 100000
  )
```




## Rates of DHB Total by Age groups (Total pop)
```{r}
# Total fully vaccinated
TFVacc_DHB_SFtotal.df <- read_excel("VaccinationDataR Updated HSU2021.xlsx", sheet = "TotalFullVacc")
TFVacc_DHB_SFtotal.df <- subset(TFVacc_DHB_SFtotal.df, Group != "Total" & Group != "Male" & DHB == "Total")

TFVacc_DHB_SFtotal.df <- pivot_longer(TFVacc_DHB_SFtotal.df, cols = 3, values_to = "Total") # changing from rows to column
TFVacc_DHB_SFtotal.df <- pivot_longer(TFVacc_DHB_SFtotal.df, cols = 3:19, names_to = "AgeGroup", values_to = "Count") # changing from rows to column

TFVacc_DHB_SFtotal.df <- TFVacc_DHB_SFtotal.df[, c(1, 5, 6, 4)] # rearranging columns to match Daniel's example below



# Using HSU Weights


HSU_TFVacc_DHB_SFtot.df <- left_join(TFVacc_DHB_SFtotal.df, HSUn.df, by = "AgeGroup")


## Calculate the age-specific rates for each age group for total regions
alpha <- 0.05 # added this in for 95% CI
HSU_TFVacc_DHB_SFtot.df <- HSU_TFVacc_DHB_SFtot.df %>%
  mutate(
    Rate = Count / Weights,
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Total^2

    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE)) * 100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance)) * 100000,
    Rate_Gamma1Lwr = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights) * 100000,
    Rate_Gamma1Upr = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights) * 100000
  )


# Using ERP Weights


ERP_TFVacc_DHB_SFtot.df <- left_join(TFVacc_DHB_SFtotal.df, ERPn.df, by = "AgeGroup")


## Calculate the age-specific rates for each age group for total regions
alpha <- 0.05 # added this in for 95% CI
ERP_TFVacc_DHB_SFtot.df <- ERP_TFVacc_DHB_SFtot.df %>%
  mutate(
    Rate = Count / Weights,
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Total^2

    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE)) * 100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance)) * 100000,
    Rate_Gamma1Lwr = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights) * 100000,
    Rate_Gamma1Upr = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights) * 100000
  )
```


## Rates of DHB Total by Age groups (M훮ori pop)
```{r}
# Total fully vaccinated
MFVacc_DHB_SFtotal.df <- read_excel("VaccinationDataR Updated HSU2021.xlsx", sheet = "MaoriFullVacc")
MFVacc_DHB_SFtotal.df <- subset(MFVacc_DHB_SFtotal.df, Group != "Total" & Group != "Male" & DHB == "Total")

MFVacc_DHB_SFtotal.df <- pivot_longer(MFVacc_DHB_SFtotal.df, cols = 3, values_to = "Total") # changing from rows to column
MFVacc_DHB_SFtotal.df <- pivot_longer(MFVacc_DHB_SFtotal.df, cols = 3:19, names_to = "AgeGroup", values_to = "Count") # changing from rows to column

MFVacc_DHB_SFtotal.df <- MFVacc_DHB_SFtotal.df[, c(1, 5, 6, 4)] # rearranging columns to match Daniel's example below



# Using HSU Weights


HSU_MFVacc_DHB_SFtot.df <- left_join(MFVacc_DHB_SFtotal.df, HSUMn.df, by = "AgeGroup")


## Calculate the age-specific rates for each age group for total regions
alpha <- 0.05 # added this in for 95% CI
HSU_MFVacc_DHB_SFtot.df <- HSU_MFVacc_DHB_SFtot.df %>%
  mutate(
    Rate = Count / Weights,
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Total^2

    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE)) * 100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance)) * 100000,
    Rate_Gamma1Lwr = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights) * 100000,
    Rate_Gamma1Upr = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights) * 100000
  )


# Using ERP Weights


ERP_MFVacc_DHB_SFtot.df <- left_join(MFVacc_DHB_SFtotal.df, ERPMn.df, by = "AgeGroup")


## Calculate the age-specific rates for each age group for total regions
alpha <- 0.05 # added this in for 95% CI
ERP_MFVacc_DHB_SFtot.df <- ERP_MFVacc_DHB_SFtot.df %>%
  mutate(
    Rate = Count / Weights,
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Total^2

    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE)) * 100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance)) * 100000,
    Rate_Gamma1Lwr = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights) * 100000,
    Rate_Gamma1Upr = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights) * 100000
  )
```


```{r,fig.height= 10, fig.width= 10}

level_order <- c("5-11", "12-17", "18-24", "25-29", "30-34", "35-39", "40-44", "45-49", "50-54", "55-59", "60-64", "65-69", "70-74", "75-79", "80-84", "85-89", "90+")


HSUvsERP_TFVacc_DHB_SFtot.df <- rbind(
  data.frame(HSU_TFVacc_DHB_SFtot.df, population = "HSU"),
  data.frame(ERP_TFVacc_DHB_SFtot.df, population = "ERP")
)

ggplot(subset(HSUvsERP_TFVacc_DHB_SFtot.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Total Females Fully Vaccinated by Age Groups") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}

# pdf(file="Total Females Fully Vaccinated by Age Groups.pdf", width = 10, height = 10)

ggplot(subset(HSUvsERP_TFVacc_DHB_SFtot.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Total Females Fully Vaccinated by Age Groups") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```

```{r}

HSUvsERP_MFVacc_DHB_SFtot.df <- rbind(
  data.frame(HSU_MFVacc_DHB_SFtot.df, population = "HSU"),
  data.frame(ERP_MFVacc_DHB_SFtot.df, population = "ERP")
)

ggplot(subset(HSUvsERP_MFVacc_DHB_SFtot.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Females Fully Vaccinated by Age Groups") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}
# pdf(file="Maori Females Fully Vaccinated by Age Groups.pdf", width = 10, height = 10)

ggplot(subset(HSUvsERP_MFVacc_DHB_SFtot.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Females Fully Vaccinated by Age Groups") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```

## Total Vaccinations RR DHB total by agegroups

## code for setting HSU as baseline for Total Vaccinations

```{r}

HSU_TFVacc_SFbaseline.total <- HSU_TFVacc_DHB_SFtot.df
ERP_TFVacc_SFpopulation.total <- ERP_TFVacc_DHB_SFtot.df

## Rename variables so we can use them after joining to the other dataset (otherwise we get Rate.x and Rate.y which is a bit confusing).
HSU_TFVacc_SFbaseline.total <- HSU_TFVacc_SFbaseline.total %>%
  dplyr::rename(
    RateBaseline = Rate,
    VarianceBaseline = Variance,
    # W_meanBaseline   = W_mean,
    RateBaselineLwr = Rate_KeyfitzLwr,
    RateBaselineUpr = Rate_KeyfitzUpr
  ) %>%
  dplyr::mutate(
    RRVarBaseline = ((Total - Count) / Total) / Count,
    ARVarBaseline = VarianceBaseline
  ) %>%
  dplyr::select(DHB, AgeGroup, RateBaseline, RRVarBaseline, ARVarBaseline, VarianceBaseline, RateBaselineLwr, RateBaselineUpr)


HSU_TFVacc_SFbaseline.other <- HSU_TFVacc_SFnontot.df
ERP_TFVacc_SFpopulation.other <- ERP_TFVacc_SFnontot.df



HSU_TFVacc_SFbaseline.other <- HSU_TFVacc_SFbaseline.other %>%
  dplyr::mutate(
    RateBaseline = Rate,
    RRVarBaseline = (1 / Count - 1 / Total),
    CountBaseline = Count,
    TotalBaseline = Total,
    RateBaselineLwr = Rate_KeyfitzLwr,
    RateBaselineUpr = Rate_KeyfitzUpr
  ) %>%
  dplyr::select(DHB, AgeGroup, RateBaseline, RRVarBaseline, CountBaseline, TotalBaseline, RateBaselineLwr, RateBaselineUpr)

## Join the baseline and other population datasets, calculating the RR and asssociated CI
ERP_TFVacc_SFpopulation.other <- ERP_TFVacc_SFpopulation.other %>%
  dplyr::left_join(HSU_TFVacc_SFbaseline.other, by = c("DHB", "AgeGroup")) %>%
  dplyr::mutate(
    RelativeRisk = Rate / RateBaseline,
    AttributableRisk = Rate - RateBaseline,
    # RRVar = (1 / Count) * ((Total - Count) / Total),
    RRVar = (1 / Count - 1 / Total),
    RelativeRiskLwr = exp(log(RelativeRisk) - 1.96 * sqrt(RRVar + RRVarBaseline)),
    RelativeRiskUpr = exp(log(RelativeRisk) + 1.96 * sqrt(RRVar + RRVarBaseline)),
    # ARVar = Rate * (1 - Rate) * (1 / Total + 1 / TotalBaseline),
    ARVar = (Count + CountBaseline) / (Total + TotalBaseline) * (1 - (Count + CountBaseline) / (Total + TotalBaseline)) * (1 / Total + 1 / TotalBaseline),
    AttributableRiskLwr = AttributableRisk - 1.96 * sqrt(ARVar),
    AttributableRiskUpr = AttributableRisk + 1.96 * sqrt(ARVar)
  ) %>%
  dplyr::select(-RRVarBaseline, -RRVar, -ARVar, -CountBaseline, -TotalBaseline, -RateBaselineLwr, -RateBaselineUpr)

TFVacc_DHB_SFpopulation.df <- ERP_TFVacc_SFpopulation.total %>%
  dplyr::left_join(HSU_TFVacc_SFbaseline.total, by = c("DHB", "AgeGroup")) %>%
  dplyr::mutate(
    RelativeRisk = Rate / RateBaseline,
    RRVar = ((Total - Count) / Total) / Count,
    RelativeRiskLwr = exp(log(RelativeRisk) - 1.96 * sqrt(RRVar + RRVarBaseline)),
    RelativeRiskUpr = exp(log(RelativeRisk) + 1.96 * sqrt(RRVar + RRVarBaseline)),
    AttributableRisk = Rate - RateBaseline,
    ARVar = Variance,
    AttributableRiskLwr = AttributableRisk - 1.96 * sqrt(ARVar + ARVarBaseline),
    AttributableRiskUpr = AttributableRisk + 1.96 * sqrt(ARVar + ARVarBaseline)
  ) %>%
  dplyr::select(-RRVarBaseline, -RRVar, -ARVarBaseline, -ARVar) %>%
  dplyr::bind_rows(ERP_TFVacc_SFpopulation.other)
```

## Rate ratio for Fully Vaccinated Rates by grouped DHB with 95% CI's
```{r, fig.height= 10, fig.width= 10}

ggplot(subset(TFVacc_DHB_SFpopulation.df, DHB == "Total"), aes(x = factor(AgeGroup, level = level_order), y = RelativeRisk, fill = RelativeRisk)) +
  geom_col(fill = "Steel Blue 2") +
  geom_errorbar(aes(min = RelativeRiskLwr, ymax = RelativeRiskUpr), width = 0.5) +
  plot_annotation(title = "Total Females Fully Vaccinated Rate Ratio by Age Group (HSU as baseline)") +
  labs(
    y = "Rate Ratio",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}
# pdf(file="Total Females Fully Vaccinated Rate Ratio by Age Group (HSU as baseline).pdf", width = 10, height = 10)


ggplot(subset(TFVacc_DHB_SFpopulation.df, DHB == "Total"), aes(x = factor(AgeGroup, level = level_order), y = RelativeRisk, fill = RelativeRisk)) +
  geom_col(fill = "Steel Blue 2") +
  geom_errorbar(aes(min = RelativeRiskLwr, ymax = RelativeRiskUpr), width = 0.5) +
  plot_annotation(title = "Total Females Fully Vaccinated Rate Ratio by Age Group (HSU as baseline)") +
  labs(
    y = "Rate Ratio",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```


## code for setting HSU as baseline for M훮ori Vaccinations

```{r}

HSU_MFVacc_SFbaseline.total <- HSU_MFVacc_DHB_SFtot.df
ERP_MFVacc_SFpopulation.total <- ERP_MFVacc_DHB_SFtot.df

## Rename variables so we can use them after joining to the other dataset (otherwise we get Rate.x and Rate.y which is a bit confusing).
HSU_MFVacc_SFbaseline.total <- HSU_MFVacc_SFbaseline.total %>%
  dplyr::rename(
    RateBaseline = Rate,
    VarianceBaseline = Variance,
    # W_meanBaseline   = W_mean,
    RateBaselineLwr = Rate_KeyfitzLwr,
    RateBaselineUpr = Rate_KeyfitzUpr
  ) %>%
  dplyr::mutate(
    RRVarBaseline = ((Total - Count) / Total) / Count,
    ARVarBaseline = VarianceBaseline
  ) %>%
  dplyr::select(DHB, AgeGroup, RateBaseline, RRVarBaseline, ARVarBaseline, VarianceBaseline, RateBaselineLwr, RateBaselineUpr)


HSU_MFVacc_SFbaseline.other <- HSU_MFVacc_SFnontot.df
ERP_MFVacc_SFpopulation.other <- ERP_MFVacc_SFnontot.df



HSU_MFVacc_SFbaseline.other <- HSU_MFVacc_SFbaseline.other %>%
  dplyr::mutate(
    RateBaseline = Rate,
    RRVarBaseline = (1 / Count - 1 / Total),
    CountBaseline = Count,
    TotalBaseline = Total,
    RateBaselineLwr = Rate_KeyfitzLwr,
    RateBaselineUpr = Rate_KeyfitzUpr
  ) %>%
  dplyr::select(DHB, AgeGroup, RateBaseline, RRVarBaseline, CountBaseline, TotalBaseline, RateBaselineLwr, RateBaselineUpr)

## Join the baseline and other population datasets, calculating the RR and asssociated CI
ERP_MFVacc_SFpopulation.other <- ERP_MFVacc_SFpopulation.other %>%
  dplyr::left_join(HSU_MFVacc_SFbaseline.other, by = c("DHB", "AgeGroup")) %>%
  dplyr::mutate(
    RelativeRisk = Rate / RateBaseline,
    AttributableRisk = Rate - RateBaseline,
    # RRVar = (1 / Count) * ((Total - Count) / Total),
    RRVar = (1 / Count - 1 / Total),
    RelativeRiskLwr = exp(log(RelativeRisk) - 1.96 * sqrt(RRVar + RRVarBaseline)),
    RelativeRiskUpr = exp(log(RelativeRisk) + 1.96 * sqrt(RRVar + RRVarBaseline)),
    # ARVar = Rate * (1 - Rate) * (1 / Total + 1 / TotalBaseline),
    ARVar = (Count + CountBaseline) / (Total + TotalBaseline) * (1 - (Count + CountBaseline) / (Total + TotalBaseline)) * (1 / Total + 1 / TotalBaseline),
    AttributableRiskLwr = AttributableRisk - 1.96 * sqrt(ARVar),
    AttributableRiskUpr = AttributableRisk + 1.96 * sqrt(ARVar)
  ) %>%
  dplyr::select(-RRVarBaseline, -RRVar, -ARVar, -CountBaseline, -TotalBaseline, -RateBaselineLwr, -RateBaselineUpr)

MFVacc_DHB_SFpopulation.df <- ERP_MFVacc_SFpopulation.total %>%
  dplyr::left_join(HSU_MFVacc_SFbaseline.total, by = c("DHB", "AgeGroup")) %>%
  dplyr::mutate(
    RelativeRisk = Rate / RateBaseline,
    RRVar = ((Total - Count) / Total) / Count,
    RelativeRiskLwr = exp(log(RelativeRisk) - 1.96 * sqrt(RRVar + RRVarBaseline)),
    RelativeRiskUpr = exp(log(RelativeRisk) + 1.96 * sqrt(RRVar + RRVarBaseline)),
    AttributableRisk = Rate - RateBaseline,
    ARVar = Variance,
    AttributableRiskLwr = AttributableRisk - 1.96 * sqrt(ARVar + ARVarBaseline),
    AttributableRiskUpr = AttributableRisk + 1.96 * sqrt(ARVar + ARVarBaseline)
  ) %>%
  dplyr::select(-RRVarBaseline, -RRVar, -ARVarBaseline, -ARVar) %>%
  dplyr::bind_rows(ERP_MFVacc_SFpopulation.other)
```

## Rate ratio for Maori Females Fully Vaccinated Rates by grouped DHB with 95% CI's
```{r, fig.height= 10, fig.width= 10}


ggplot(subset(MFVacc_DHB_SFpopulation.df, DHB == "Total"), aes(x = factor(AgeGroup, level = level_order), y = RelativeRisk, fill = RelativeRisk)) +
  geom_col(fill = "Steel Blue 2") +
  geom_errorbar(aes(min = RelativeRiskLwr, ymax = RelativeRiskUpr), width = 0.5) +
  plot_annotation(title = "Maori Females Fully Vaccinated Rate Ratio by Age Group (HSU as baseline)") +
  labs(
    y = "Rate Ratio",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}
# pdf(file="Maori Females Fully Vaccinated Rate Ratio by Age Group (HSU as baseline).pdf", width = 10, height = 10)


ggplot(subset(MFVacc_DHB_SFpopulation.df, DHB == "Total"), aes(x = factor(AgeGroup, level = level_order), y = RelativeRisk, fill = RelativeRisk)) +
  geom_col(fill = "Steel Blue 2") +
  geom_errorbar(aes(min = RelativeRiskLwr, ymax = RelativeRiskUpr), width = 0.5) +
  plot_annotation(title = "Maori Females Fully Vaccinated Rate Ratio by Age Group (HSU as baseline)") +
  labs(
    y = "Rate Ratio",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```

```{r, fig.height= 10, fig.width= 10}

HSUvsERP_TFVacc_SFnontot.df <- rbind(
  data.frame(HSU_TFVacc_SFnontot.df, population = "HSU"),
  data.frame(ERP_TFVacc_SFnontot.df, population = "ERP")
)

ggplot(subset(HSUvsERP_TFVacc_SFnontot.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Total Females Fully Vaccinated by Age Group & DHB") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}
# pdf(file="Total Females Fully Vaccinated by Age Group & DHB Fullplot.pdf", width = 10, height = 10)

ggplot(subset(HSUvsERP_TFVacc_SFnontot.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Total Females Fully Vaccinated by Age Group & DHB") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```

```{r, fig.height= 10, fig.width= 10}
HSU_MFVacc_nontot_high1.df <- HSU_MFVacc_SFnontot.df[HSU_MFVacc_SFnontot.df$DHB %in% c("Northland", "Waikato", "Counties Manukau", "Bay of Plenty"), ]
HSU_MFVacc_nontot_high2.df <- HSU_MFVacc_SFnontot.df[HSU_MFVacc_SFnontot.df$DHB %in% c("Waitemata", "Lakes", "Tairawhiti", "Hawkes Bay"), ]
HSU_MFVacc_nontot_mid1.df <- HSU_MFVacc_SFnontot.df[HSU_MFVacc_SFnontot.df$DHB %in% c("Canterbury", "Southern", "Capital and Coast", "Auckland"), ]
HSU_MFVacc_nontot_mid2.df <- HSU_MFVacc_SFnontot.df[HSU_MFVacc_SFnontot.df$DHB %in% c("MidCentral", "Hutt Valley", "Taranaki", "Whanganui"), ]

HSU_MFVacc_nontot_low.df <- HSU_MFVacc_SFnontot.df[HSU_MFVacc_SFnontot.df$DHB %in% c("South Canterbury", "West Coast", "Nelson Marlborough", "Wairarapa"), ]


ERP_MFVacc_nontot_high1.df <- ERP_MFVacc_SFnontot.df[ERP_MFVacc_SFnontot.df$DHB %in% c("Northland", "Waikato", "Counties Manukau", "Bay of Plenty"), ]
ERP_MFVacc_nontot_high2.df <- ERP_MFVacc_SFnontot.df[ERP_MFVacc_SFnontot.df$DHB %in% c("Waitemata", "Lakes", "Tairawhiti", "Hawkes Bay"), ]
ERP_MFVacc_nontot_mid1.df <- ERP_MFVacc_SFnontot.df[ERP_MFVacc_SFnontot.df$DHB %in% c("Canterbury", "Southern", "Capital and Coast", "Auckland"), ]

ERP_MFVacc_nontot_mid2.df <- ERP_MFVacc_SFnontot.df[ERP_MFVacc_SFnontot.df$DHB %in% c("MidCentral", "Hutt Valley", "Taranaki", "Whanganui"), ]
ERP_MFVacc_nontot_low.df <- ERP_MFVacc_SFnontot.df[ERP_MFVacc_SFnontot.df$DHB %in% c("South Canterbury", "West Coast", "Nelson Marlborough", "Wairarapa"), ]



HSUvsERP_MFVacc_nontot_high1.df <- rbind(
  data.frame(HSU_MFVacc_nontot_high1.df, population = "HSU"),
  data.frame(ERP_MFVacc_nontot_high1.df, population = "ERP")
)

ggplot(subset(HSUvsERP_MFVacc_nontot_high1.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Females Fully Vaccinated by Age Group & DHB") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}

# pdf(file="Maori Females Fully Vaccinated by Age Group & DHB high1.pdf", width = 10, height = 10)


ggplot(subset(HSUvsERP_MFVacc_nontot_high1.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Females Fully Vaccinated by Age Group & DHB") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```

```{r}
HSUvsERP_MFVacc_nontot_high2.df <- rbind(
  data.frame(HSU_MFVacc_nontot_high2.df, population = "HSU"),
  data.frame(ERP_MFVacc_nontot_high2.df, population = "ERP")
)

ggplot(subset(HSUvsERP_MFVacc_nontot_high2.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Females Fully Vaccinated by Age Group & DHB") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}

# pdf(file="Maori Females Fully Vaccinated by Age Group & DHB high2.pdf", width = 10, height = 10)


ggplot(subset(HSUvsERP_MFVacc_nontot_high2.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Females Fully Vaccinated by Age Group & DHB") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```

```{r}

HSUvsERP_MFVacc_nontot_mid1.df <- rbind(
  data.frame(HSU_MFVacc_nontot_mid1.df, population = "HSU"),
  data.frame(ERP_MFVacc_nontot_mid1.df, population = "ERP")
)

ggplot(subset(HSUvsERP_MFVacc_nontot_mid1.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Females Fully Vaccinated by Age Group & DHB") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}

# pdf(file="Maori Females Fully Vaccinated by Age Group & DHB mid1.pdf", width = 10, height = 10)


ggplot(subset(HSUvsERP_MFVacc_nontot_mid1.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Females Fully Vaccinated by Age Group & DHB") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```

```{r}
HSUvsERP_MFVacc_nontot_mid2.df <- rbind(
  data.frame(HSU_MFVacc_nontot_mid2.df, population = "HSU"),
  data.frame(ERP_MFVacc_nontot_mid2.df, population = "ERP")
)

ggplot(subset(HSUvsERP_MFVacc_nontot_mid2.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Females Fully Vaccinated by Age Group & DHB") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}

# pdf(file="Maori Females Fully Vaccinated by Age Group & DHB mid2.pdf", width = 10, height = 10)


ggplot(subset(HSUvsERP_MFVacc_nontot_mid2.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Females Fully Vaccinated by Age Group & DHB") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```

```{r}
HSUvsERP_MFVacc_nontot_low.df <- rbind(
  data.frame(HSU_MFVacc_nontot_low.df, population = "HSU"),
  data.frame(ERP_MFVacc_nontot_low.df, population = "ERP")
)

ggplot(subset(HSUvsERP_MFVacc_nontot_low.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Females Fully Vaccinated by Age Group & DHB") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}

# pdf(file="Maori Females Fully Vaccinated by Age Group & DHB low.pdf", width = 10, height = 10)

ggplot(subset(HSUvsERP_MFVacc_nontot_low.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Females Fully Vaccinated by Age Group & DHB") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```

## presenting highest diff in comparison to M훮ori males
```{r, fig.height= 10, fig.width= 10}
# separated by rate levels

HSU_MFVacc_nontot_highestdiff.df <- HSU_MFVacc_SFnontot.df[HSU_MFVacc_SFnontot.df$DHB %in% c("Counties Manukau"), ]

ERP_MFVacc_nontot_highestdiff.df <- ERP_MFVacc_SFnontot.df[ERP_MFVacc_SFnontot.df$DHB %in% c("Counties Manukau"), ]


HSUvsERP_MFVacc_highestdiff.df <- rbind(
  data.frame(HSU_MFVacc_nontot_highestdiff.df, population = "HSU"),
  data.frame(ERP_MFVacc_nontot_highestdiff.df, population = "ERP")
)

ggplot(subset(HSUvsERP_MFVacc_highestdiff.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Females Fully Vaccinated by Age Group for Counties Manukau DHB (Rates per 100,000)") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}
# pdf(file="Maori Females Fully Vaccinated by Age Group & highest diff DHB.pdf", width = 10, height = 10)

ggplot(subset(HSUvsERP_MFVacc_highestdiff.df), aes(x = factor(AgeGroup, level = level_order), y = RateMult, fill = population, group = population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_errorbar(aes(ymin = Rate_Gamma1Lwr, ymax = Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Females Fully Vaccinated by Age Group for Counties Manukau DHB (Rates per 100,000)") +
  labs(
    y = "Rate per 100,000",
    x = "Age Groups"
  ) &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```


