---
title: "Vaccination Rates (Males)"
author: "Tori Diamond"
date: '2022-06-23'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl); library(magrittr); library(dplyr); library(tidyr); library(reshape2); library(ggplot2); library(patchwork);library(ggnewscale)
```

## Creating weights for each population type
```{r}
## creating weights df
weights.df <- read_excel("Weights.xlsx", sheet = "HSU&ERP")

#HSU total weights
#using numbers
HSUn.df <- weights.df[-c(2:12),]
HSUn.df <- pivot_longer(HSUn.df, cols = 3:20, names_to = "AgeGroup", values_to = "Weights" ) #changing from rows to column
HSUn.df <- HSUn.df[,c(3,4)] #only showing weights by age-groups

#HSU Māori weights
#using numbers
HSUMn.df <- weights.df[-c(1:2,4:12),]
HSUMn.df <- pivot_longer(HSUMn.df, cols = 3:20, names_to = "AgeGroup", values_to = "Weights" ) #changing from rows to column
HSUMn.df <- HSUMn.df[,c(3,4)] #only showing weights by age-groups

#HSU NonMāori weights
#using numbers
HSUNMn.df <- weights.df[-c(1:4,6:12),]
HSUNMn.df <- pivot_longer(HSUNMn.df, cols = 3:20, names_to = "AgeGroup", values_to = "Weights" ) #changing from rows to column
HSUNMn.df <- HSUNMn.df[,c(3,4)] #only showing weights by age-groups


#ERP total weights
#using numbers
ERPn.df <- weights.df[-c(1:6,8:12),]
ERPn.df <- pivot_longer(ERPn.df, cols = 3:20, names_to = "AgeGroup", values_to = "Weights" ) #changing from rows to column
ERPn.df <- ERPn.df[,c(3,4)] #only showing weights by age-groups

#ERP Māori weights
#using numbers
ERPMn.df <- weights.df[-c(1:8,10:12),]
ERPMn.df <- pivot_longer(ERPMn.df, cols = 3:20, names_to = "AgeGroup", values_to = "Weights" ) #changing from rows to column
ERPMn.df <- ERPMn.df[,c(3,4)] #only showing weights by age-groups

#ERP NonMāori weights
#using numbers
ERPNMn.df <- weights.df[-c(1:10,12),]
ERPNMn.df <- pivot_longer(ERPNMn.df, cols = 3:20, names_to = "AgeGroup", values_to = "Weights" ) #changing from rows to column
ERPNMn.df <- ERPNMn.df[,c(3,4)] #only showing weights by age-groups


```

## Total Fully Vaccinated Rates

```{r}
# Total fully vaccinated
TFVacc_SMnontotal.df <- read_excel("VaccinationDataR Updated HSU2021.xlsx", sheet = "TotalFullVacc")
TFVacc_SMnontotal.df<- subset(TFVacc_SMnontotal.df, Group!="Total" & Group!="Female" & DHB!="Total")

TFVacc_SMnontotal.df <- pivot_longer(TFVacc_SMnontotal.df, cols = 4:20, names_to = "AgeGroup", values_to = "Count" ) #changing from rows to column
TFVacc_SMnontotal.df <- TFVacc_SMnontotal.df[,c(1,4,5,3)] #rearranging columns to match Daniel's example below


# Using HSU Weights

## Join on the standard population weights (adds in a column called "Weights")
HSU_TFVacc_SMnontot.df <- left_join(TFVacc_SMnontotal.df, HSUn.df, by = "AgeGroup")


## Create a dataset for the total of each DHB (all age groups summed), doesn't include all DHB named 'Total'
HSU_TFVacc_SMtot.df <- HSU_TFVacc_SMnontot.df %>%
  group_by(DHB) %>%
  summarise(
    AgeGroup = "Total",
    Count = sum(Count), Total = sum(Weights) #sum weights as want to divide by total HSU population for Rate
  )

## Calculate the age-specific rates for each age group in each year
alpha = 0.05 #added this in for 95% CI
HSU_TFVacc_SMnontot.df <- HSU_TFVacc_SMnontot.df %>%
  mutate(
    Rate     = Count / Weights, #dividing by age-band population for rate
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Weights^2
    
    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE))*100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance))*100000,
    
    Rate_Gamma1Lwr  = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights)*100000,
    Rate_Gamma1Upr  = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights)*100000
  )

# Using ERP Weights

## Join on the standard population weights (adds in a column called "Weights")
ERP_TFVacc_SMnontot.df <- left_join(TFVacc_SMnontotal.df, ERPn.df, by = "AgeGroup")


## Create a dataset for the total of each DHB (all age groups summed), doesn't include all DHB named 'Total'
ERP_TFVacc_SMtot.df <- ERP_TFVacc_SMnontot.df %>%
  group_by(DHB) %>%
  summarise(
    AgeGroup = "Total",
    Count = sum(Count), Total = sum(Weights) #sum weights as want to divide by total HSU population for Rate
  )

## Calculate the age-specific rates for each age group in each year
alpha = 0.05 #added this in for 95% CI
ERP_TFVacc_SMnontot.df <- ERP_TFVacc_SMnontot.df %>%
  mutate(
    Rate     = Count / Weights, #dividing by age-band population for rate
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Weights^2
    
    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE))*100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance))*100000,
    
    Rate_Gamma1Lwr  = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights)*100000,
    Rate_Gamma1Upr  = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights)*100000
  )

```


## Māori Fully Vaccinated Rates

```{r}
# Total fully vaccinated
MFVacc_SMnontotal.df <- read_excel("VaccinationDataR Updated HSU2021.xlsx", sheet = "MaoriFullVacc")
MFVacc_SMnontotal.df<- subset(MFVacc_SMnontotal.df, Group!="Total" & Group!="Female" & DHB!="Total")

MFVacc_SMnontotal.df <- pivot_longer(MFVacc_SMnontotal.df, cols = 4:20, names_to = "AgeGroup", values_to = "Count" ) #changing from rows to column
MFVacc_SMnontotal.df <- MFVacc_SMnontotal.df[,c(1,4,5,3)] #rearranging columns to match Daniel's example below


# Using HSU Weights

## Join on the standard population weights (adds in a column called "Weights")
HSU_MFVacc_SMnontot.df <- left_join(MFVacc_SMnontotal.df, HSUMn.df, by = "AgeGroup")


## Create a dataset for the total of each DHB (all age groups summed), doesn't include all DHB named 'Total'
HSU_MFVacc_SMtot.df <- HSU_MFVacc_SMnontot.df %>%
  group_by(DHB) %>%
  summarise(
    AgeGroup = "Total",
    Count = sum(Count), Total = sum(Weights) #sum weights as want to divide by total HSU population for Rate
  )

## Calculate the age-specific rates for each age group in each year
alpha = 0.05 #added this in for 95% CI
HSU_MFVacc_SMnontot.df <- HSU_MFVacc_SMnontot.df %>%
  mutate(
    Rate     = Count / Weights, #dividing by age-band population for rate
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Weights^2
    
    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE))*100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance))*100000,
    
    Rate_Gamma1Lwr  = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights)*100000,
    Rate_Gamma1Upr  = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights)*100000
  )

# Using ERP Weights

## Join on the standard population weights (adds in a column called "Weights")
ERP_MFVacc_SMnontot.df <- left_join(MFVacc_SMnontotal.df, ERPMn.df, by = "AgeGroup")


## Create a dataset for the total of each DHB (all age groups summed), doesn't include all DHB named 'Total'
ERP_MFVacc_SMtot.df <- ERP_MFVacc_SMnontot.df %>%
  group_by(DHB) %>%
  summarise(
    AgeGroup = "Total",
    Count = sum(Count), Total = sum(Weights) #sum weights as want to divide by total HSU population for Rate
  )

## Calculate the age-specific rates for each age group in each year
alpha = 0.05 #added this in for 95% CI
ERP_MFVacc_SMnontot.df <- ERP_MFVacc_SMnontot.df %>%
  mutate(
    Rate     = Count / Weights, #dividing by age-band population for rate
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Weights^2
    
    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE))*100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance))*100000,
    
    Rate_Gamma1Lwr  = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights)*100000,
    Rate_Gamma1Upr  = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights)*100000
  )

```

## Non-Māori Fully Vaccinated Rates

```{r}
# Total fully vaccinated
NMFVacc_SMnontotal.df <- read_excel("VaccinationDataR Updated HSU2021.xlsx", sheet = "NonMaoriFullVacc")
NMFVacc_SMnontotal.df<- subset(NMFVacc_SMnontotal.df, Group!="Total" & Group!="Female" & DHB!="Total")

NMFVacc_SMnontotal.df <- pivot_longer(NMFVacc_SMnontotal.df, cols = 4:20, names_to = "AgeGroup", values_to = "Count" ) #changing from rows to column
NMFVacc_SMnontotal.df <- NMFVacc_SMnontotal.df[,c(1,4,5,3)] #rearranging columns to match Daniel's example below


# Using HSU Weights

## Join on the standard population weights (adds in a column called "Weights")
HSU_NMFVacc_SMnontot.df <- left_join(NMFVacc_SMnontotal.df, HSUNMn.df, by = "AgeGroup")


## Create a dataset for the total of each DHB (all age groups summed), doesn't include all DHB named 'Total'
HSU_NMFVacc_SMtot.df <- HSU_NMFVacc_SMnontot.df %>%
  group_by(DHB) %>%
  summarise(
    AgeGroup = "Total",
    Count = sum(Count), Total = sum(Weights) #sum weights as want to divide by total HSU population for Rate
  )

## Calculate the age-specific rates for each age group in each year
alpha = 0.05 #added this in for 95% CI
HSU_NMFVacc_SMnontot.df <- HSU_NMFVacc_SMnontot.df %>%
  mutate(
    Rate     = Count / Weights, #dividing by age-band population for rate
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Weights^2
    
    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE))*100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance))*100000,
    
    Rate_Gamma1Lwr  = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights)*100000,
    Rate_Gamma1Upr  = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights)*100000
  )

# Using ERP Weights

## Join on the standard population weights (adds in a column called "Weights")
ERP_NMFVacc_SMnontot.df <- left_join(NMFVacc_SMnontotal.df, ERPNMn.df, by = "AgeGroup")


## Create a dataset for the total of each DHB (all age groups summed), doesn't include all DHB named 'Total'
ERP_NMFVacc_SMtot.df <- ERP_NMFVacc_SMnontot.df %>%
  group_by(DHB) %>%
  summarise(
    AgeGroup = "Total",
    Count = sum(Count), Total = sum(Weights) #sum weights as want to divide by total HSU population for Rate
  )

## Calculate the age-specific rates for each age group in each year
alpha = 0.05 #added this in for 95% CI
ERP_NMFVacc_SMnontot.df <- ERP_NMFVacc_SMnontot.df %>%
  mutate(
    Rate     = Count / Weights, #dividing by age-band population for rate
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Weights^2
    
    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE))*100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance))*100000,
    
    Rate_Gamma1Lwr  = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights)*100000,
    Rate_Gamma1Upr  = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights)*100000
  )

```





## Rates of DHB Total by Age groups (Total pop)
```{r}
# Total fully vaccinated
TFVacc_DHB_SMtotal.df <- read_excel("VaccinationDataR Updated HSU2021.xlsx", sheet = "TotalFullVacc")
TFVacc_DHB_SMtotal.df<- subset(TFVacc_DHB_SMtotal.df, Group!="Total" & Group!="Female" & DHB=="Total")

TFVacc_DHB_SMtotal.df <- pivot_longer(TFVacc_DHB_SMtotal.df, cols = 3, values_to = "Total" ) #changing from rows to column
TFVacc_DHB_SMtotal.df <- pivot_longer(TFVacc_DHB_SMtotal.df, cols = 3:19, names_to = "AgeGroup", values_to = "Count" ) #changing from rows to column

TFVacc_DHB_SMtotal.df <- TFVacc_DHB_SMtotal.df[,c(1,5,6,4)] #rearranging columns to match Daniel's example below



# Using HSU Weights


HSU_TFVacc_DHB_SMtot.df <- left_join(TFVacc_DHB_SMtotal.df, HSUn.df, by = "AgeGroup")


## Calculate the age-specific rates for each age group for total regions
alpha = 0.05 #added this in for 95% CI
HSU_TFVacc_DHB_SMtot.df <- HSU_TFVacc_DHB_SMtot.df %>%
  mutate(
    Rate     = Count / Weights,
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Total^2
    
    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE))*100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance))*100000,
    
    Rate_Gamma1Lwr  = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights)*100000,
    Rate_Gamma1Upr  = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights)*100000
  )


# Using ERP Weights


ERP_TFVacc_DHB_SMtot.df <- left_join(TFVacc_DHB_SMtotal.df, ERPn.df, by = "AgeGroup")


## Calculate the age-specific rates for each age group for total regions
alpha = 0.05 #added this in for 95% CI
ERP_TFVacc_DHB_SMtot.df <- ERP_TFVacc_DHB_SMtot.df %>%
  mutate(
    Rate     = Count / Weights,
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Total^2
    
    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE))*100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance))*100000,
    
    Rate_Gamma1Lwr  = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights)*100000,
    Rate_Gamma1Upr  = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights)*100000
  )

```


## Rates of DHB Total by Age groups (Māori pop)
```{r}
# Total fully vaccinated
MFVacc_DHB_SMtotal.df <- read_excel("VaccinationDataR Updated HSU2021.xlsx", sheet = "MaoriFullVacc")
MFVacc_DHB_SMtotal.df<- subset(MFVacc_DHB_SMtotal.df, Group!="Total" & Group!="Female" & DHB=="Total")

MFVacc_DHB_SMtotal.df <- pivot_longer(MFVacc_DHB_SMtotal.df, cols = 3, values_to = "Total" ) #changing from rows to column
MFVacc_DHB_SMtotal.df <- pivot_longer(MFVacc_DHB_SMtotal.df, cols = 3:19, names_to = "AgeGroup", values_to = "Count" ) #changing from rows to column

MFVacc_DHB_SMtotal.df <- MFVacc_DHB_SMtotal.df[,c(1,5,6,4)] #rearranging columns to match Daniel's example below



# Using HSU Weights


HSU_MFVacc_DHB_SMtot.df <- left_join(MFVacc_DHB_SMtotal.df, HSUMn.df, by = "AgeGroup")


## Calculate the age-specific rates for each age group for total regions
alpha = 0.05 #added this in for 95% CI
HSU_MFVacc_DHB_SMtot.df <- HSU_MFVacc_DHB_SMtot.df %>%
  mutate(
    Rate     = Count / Weights,
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Total^2
    
    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE))*100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance))*100000,
    
    Rate_Gamma1Lwr  = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights)*100000,
    Rate_Gamma1Upr  = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights)*100000
  )


# Using ERP Weights


ERP_MFVacc_DHB_SMtot.df <- left_join(MFVacc_DHB_SMtotal.df, ERPMn.df, by = "AgeGroup")


## Calculate the age-specific rates for each age group for total regions
alpha = 0.05 #added this in for 95% CI
ERP_MFVacc_DHB_SMtot.df <- ERP_MFVacc_DHB_SMtot.df %>%
  mutate(
    Rate     = Count / Weights,
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Total^2
    
    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE))*100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance))*100000,
    
    Rate_Gamma1Lwr  = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights)*100000,
    Rate_Gamma1Upr  = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights)*100000
  )

```


## Rates of DHB Total by Age groups (Non-Māori pop)
```{r}
# Total fully vaccinated
NMFVacc_DHB_SMtotal.df <- read_excel("VaccinationDataR Updated HSU2021.xlsx", sheet = "NonMaoriFullVacc")
NMFVacc_DHB_SMtotal.df<- subset(NMFVacc_DHB_SMtotal.df, Group!="Total" & Group!="Female" & DHB=="Total")

NMFVacc_DHB_SMtotal.df <- pivot_longer(NMFVacc_DHB_SMtotal.df, cols = 3, values_to = "Total" ) #changing from rows to column
NMFVacc_DHB_SMtotal.df <- pivot_longer(NMFVacc_DHB_SMtotal.df, cols = 3:19, names_to = "AgeGroup", values_to = "Count" ) #changing from rows to column

NMFVacc_DHB_SMtotal.df <- NMFVacc_DHB_SMtotal.df[,c(1,5,6,4)] #rearranging columns to match Daniel's example below



# Using HSU Weights


HSU_NMFVacc_DHB_SMtot.df <- left_join(NMFVacc_DHB_SMtotal.df, HSUNMn.df, by = "AgeGroup")


## Calculate the age-specific rates for each age group for total regions
alpha = 0.05 #added this in for 95% CI
HSU_NMFVacc_DHB_SMtot.df <- HSU_NMFVacc_DHB_SMtot.df %>%
  mutate(
    Rate     = Count / Weights,
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Total^2
    
    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE))*100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance))*100000,
    
    Rate_Gamma1Lwr  = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights)*100000,
    Rate_Gamma1Upr  = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights)*100000
  )


# Using ERP Weights


ERP_NMFVacc_DHB_SMtot.df <- left_join(NMFVacc_DHB_SMtotal.df, ERPNMn.df, by = "AgeGroup")


## Calculate the age-specific rates for each age group for total regions
alpha = 0.05 #added this in for 95% CI
ERP_NMFVacc_DHB_SMtot.df <- ERP_NMFVacc_DHB_SMtot.df %>%
  mutate(
    Rate     = Count / Weights,
    RateMult = Rate * 100000,
    Variance = Rate / Weights, ## Var(R) = Count / Total^2
    
    Rate_KeyfitzLwr = (pmax(0, Rate - qnorm(1 - alpha / 2) * sqrt(Variance), na.rm = TRUE))*100000,
    Rate_KeyfitzUpr = (Rate + qnorm(1 - alpha / 2) * sqrt(Variance))*100000,
    
    Rate_Gamma1Lwr  = (0.5 * qchisq(alpha / 2, 2 * Count) / Weights)*100000,
    Rate_Gamma1Upr  = (0.5 * qchisq(1 - alpha / 2, 2 * (Count + 1)) / Weights)*100000
  )

```



```{r,fig.height= 10, fig.width= 10}

level_order <- c("5-11","12-17", "18-24", "25-29", "30-34", "35-39","40-44", "45-49", "50-54", "55-59", "60-64", "65-69", "70-74", "75-79", "80-84", "85-89", "90+")


HSUvsERP_TFVacc_DHB_SMtot.df <- rbind(
  data.frame(HSU_TFVacc_DHB_SMtot.df, population="HSU"),
  data.frame(ERP_TFVacc_DHB_SMtot.df, population="ERP")
)

ggplot(subset(HSUvsERP_TFVacc_DHB_SMtot.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Total Males Fully Vaccinated by Age Groups") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))
```


```{r, eval=FALSE}

#pdf(file="Total Males Fully Vaccinated by Age Groups.pdf", width = 10, height = 10)

ggplot(subset(HSUvsERP_TFVacc_DHB_SMtot.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Total Males Fully Vaccinated by Age Groups") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()

```


```{r}
HSUvsERP_MFVacc_DHB_SMtot.df <- rbind(
  data.frame(HSU_MFVacc_DHB_SMtot.df, population="HSU"),
  data.frame(ERP_MFVacc_DHB_SMtot.df, population="ERP")
)

ggplot(subset(HSUvsERP_MFVacc_DHB_SMtot.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Groups") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

```

```{r, eval=FALSE}

#pdf(file="Maori Males Fully Vaccinated by Age Groups.pdf", width = 10, height = 10)

ggplot(subset(HSUvsERP_MFVacc_DHB_SMtot.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Groups") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()


```


```{r}
HSUvsERP_NMFVacc_DHB_SMtot.df <- rbind(
  data.frame(HSU_NMFVacc_DHB_SMtot.df, population="HSU"),
  data.frame(ERP_NMFVacc_DHB_SMtot.df, population="ERP")
)

ggplot(subset(HSUvsERP_NMFVacc_DHB_SMtot.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Non-Maori Males Fully Vaccinated by Age Groups") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

```

```{r, eval=FALSE}

#pdf(file="Non-Maori Males Fully Vaccinated by Age Groups.pdf", width = 10, height = 10)

ggplot(subset(HSUvsERP_NMFVacc_DHB_SMtot.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Non-Maori Males Fully Vaccinated by Age Groups") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()


```






## Total Vaccinations RR DHB total by agegroups

## code for setting HSU as baseline for Total Vaccinations

```{r}

HSU_TFVacc_SMbaseline.total <- HSU_TFVacc_DHB_SMtot.df
ERP_TFVacc_SMpopulation.total <- ERP_TFVacc_DHB_SMtot.df

## Rename variables so we can use them after joining to the other dataset (otherwise we get Rate.x and Rate.y which is a bit confusing).
HSU_TFVacc_SMbaseline.total <- HSU_TFVacc_SMbaseline.total %>%
  dplyr::rename(
    RateBaseline     = Rate,
    VarianceBaseline = Variance,
    #W_meanBaseline   = W_mean,
    RateBaselineLwr = Rate_KeyfitzLwr,
    RateBaselineUpr = Rate_KeyfitzUpr
  ) %>%
  dplyr::mutate(
    RRVarBaseline = ((Total - Count) / Total) / Count,
    ARVarBaseline = VarianceBaseline
  ) %>%
  dplyr::select(DHB, AgeGroup, RateBaseline, RRVarBaseline, ARVarBaseline, VarianceBaseline, RateBaselineLwr, RateBaselineUpr)


HSU_TFVacc_SMbaseline.other <- HSU_TFVacc_SMnontot.df
ERP_TFVacc_SMpopulation.other <- ERP_TFVacc_SMnontot.df



HSU_TFVacc_SMbaseline.other <- HSU_TFVacc_SMbaseline.other %>%
  dplyr::mutate(
    RateBaseline = Rate,
    RRVarBaseline = (1 / Count - 1 / Total),
    CountBaseline = Count,
    TotalBaseline = Total,

    RateBaselineLwr = Rate_KeyfitzLwr,
    RateBaselineUpr = Rate_KeyfitzUpr
  ) %>%
  dplyr::select(DHB, AgeGroup, RateBaseline, RRVarBaseline, CountBaseline, TotalBaseline, RateBaselineLwr, RateBaselineUpr)

## Join the baseline and other population datasets, calculating the RR and asssociated CI
ERP_TFVacc_SMpopulation.other <-ERP_TFVacc_SMpopulation.other %>%
  dplyr::left_join(HSU_TFVacc_SMbaseline.other, by = c("DHB", "AgeGroup")) %>%
  dplyr::mutate(
    RelativeRisk = Rate / RateBaseline,
    AttributableRisk = Rate - RateBaseline,
    # RRVar = (1 / Count) * ((Total - Count) / Total),
    RRVar = (1 / Count - 1 / Total),
    RelativeRiskLwr = exp(log(RelativeRisk) - 1.96 * sqrt(RRVar + RRVarBaseline)),
    RelativeRiskUpr = exp(log(RelativeRisk) + 1.96 * sqrt(RRVar + RRVarBaseline)),
    # ARVar = Rate * (1 - Rate) * (1 / Total + 1 / TotalBaseline),
    ARVar = (Count + CountBaseline) / (Total + TotalBaseline) * (1 - (Count + CountBaseline) / (Total + TotalBaseline)) * (1 / Total + 1 / TotalBaseline),
    AttributableRiskLwr = AttributableRisk - 1.96 * sqrt(ARVar),
    AttributableRiskUpr = AttributableRisk + 1.96 * sqrt(ARVar)
  ) %>%
  dplyr::select(-RRVarBaseline, -RRVar, -ARVar, -CountBaseline, -TotalBaseline, -RateBaselineLwr, -RateBaselineUpr)

TFVacc_DHB_SMpopulation.df <- ERP_TFVacc_SMpopulation.total %>%
  dplyr::left_join(HSU_TFVacc_SMbaseline.total, by = c("DHB", "AgeGroup")) %>%
  dplyr::mutate(
    RelativeRisk    = Rate / RateBaseline,
    RRVar           = ((Total - Count) / Total) / Count,
    RelativeRiskLwr = exp(log(RelativeRisk) - 1.96 * sqrt(RRVar + RRVarBaseline)),
    RelativeRiskUpr = exp(log(RelativeRisk) + 1.96 * sqrt(RRVar + RRVarBaseline)),

    AttributableRisk    = Rate - RateBaseline,
    ARVar               = Variance,
    AttributableRiskLwr = AttributableRisk - 1.96 * sqrt(ARVar + ARVarBaseline),
    AttributableRiskUpr = AttributableRisk + 1.96 * sqrt(ARVar + ARVarBaseline)
  ) %>%
  dplyr::select(-RRVarBaseline, -RRVar, -ARVarBaseline, -ARVar) %>%
  dplyr::bind_rows(ERP_TFVacc_SMpopulation.other)


```

## Rate ratio for Fully Vaccinated Rates by grouped DHB with 95% CI's
```{r, fig.height= 10, fig.width= 10}

ggplot(subset(TFVacc_DHB_SMpopulation.df, DHB == "Total"), aes(x=factor(AgeGroup, level= level_order), y = RelativeRisk,fill=RelativeRisk))+
  geom_col(fill = "Steel Blue 2")+
  geom_errorbar(aes(min=RelativeRiskLwr, ymax=RelativeRiskUpr), width=0.5) +
  plot_annotation(title = "Total Males Fully Vaccinated Rate Ratio by Age Group (HSU as baseline)") +
  labs(y= "Rate Ratio",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))


```

```{r, eval=FALSE}
#pdf(file="Total Males Fully Vaccinated Rate Ratio by Age Group (HSU as baseline).pdf", width = 10, height = 10)


ggplot(subset(TFVacc_DHB_SMpopulation.df, DHB == "Total"), aes(x=factor(AgeGroup, level= level_order), y = RelativeRisk,fill=RelativeRisk))+
  geom_col(fill = "Steel Blue 2")+
  geom_errorbar(aes(min=RelativeRiskLwr, ymax=RelativeRiskUpr), width=0.5) +
  plot_annotation(title = "Total Males Fully Vaccinated Rate Ratio by Age Group (HSU as baseline)") +
  labs(y= "Rate Ratio",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```






## code for setting HSU as baseline for Māori Vaccinations

```{r}

HSU_MFVacc_SMbaseline.total <- HSU_MFVacc_DHB_SMtot.df
ERP_MFVacc_SMpopulation.total <- ERP_MFVacc_DHB_SMtot.df

## Rename variables so we can use them after joining to the other dataset (otherwise we get Rate.x and Rate.y which is a bit confusing).
HSU_MFVacc_SMbaseline.total <- HSU_MFVacc_SMbaseline.total %>%
  dplyr::rename(
    RateBaseline     = Rate,
    VarianceBaseline = Variance,
    #W_meanBaseline   = W_mean,
    RateBaselineLwr = Rate_KeyfitzLwr,
    RateBaselineUpr = Rate_KeyfitzUpr
  ) %>%
  dplyr::mutate(
    RRVarBaseline = ((Total - Count) / Total) / Count,
    ARVarBaseline = VarianceBaseline
  ) %>%
  dplyr::select(DHB, AgeGroup, RateBaseline, RRVarBaseline, ARVarBaseline, VarianceBaseline, RateBaselineLwr, RateBaselineUpr)


HSU_MFVacc_SMbaseline.other <- HSU_MFVacc_SMnontot.df
ERP_MFVacc_SMpopulation.other <- ERP_MFVacc_SMnontot.df



HSU_MFVacc_SMbaseline.other <- HSU_MFVacc_SMbaseline.other %>%
  dplyr::mutate(
    RateBaseline = Rate,
    RRVarBaseline = (1 / Count - 1 / Total),
    CountBaseline = Count,
    TotalBaseline = Total,

    RateBaselineLwr = Rate_KeyfitzLwr,
    RateBaselineUpr = Rate_KeyfitzUpr
  ) %>%
  dplyr::select(DHB, AgeGroup, RateBaseline, RRVarBaseline, CountBaseline, TotalBaseline, RateBaselineLwr, RateBaselineUpr)

## Join the baseline and other population datasets, calculating the RR and asssociated CI
ERP_MFVacc_SMpopulation.other <-ERP_MFVacc_SMpopulation.other %>%
  dplyr::left_join(HSU_MFVacc_SMbaseline.other, by = c("DHB", "AgeGroup")) %>%
  dplyr::mutate(
    RelativeRisk = Rate / RateBaseline,
    AttributableRisk = Rate - RateBaseline,
    # RRVar = (1 / Count) * ((Total - Count) / Total),
    RRVar = (1 / Count - 1 / Total),
    RelativeRiskLwr = exp(log(RelativeRisk) - 1.96 * sqrt(RRVar + RRVarBaseline)),
    RelativeRiskUpr = exp(log(RelativeRisk) + 1.96 * sqrt(RRVar + RRVarBaseline)),
    # ARVar = Rate * (1 - Rate) * (1 / Total + 1 / TotalBaseline),
    ARVar = (Count + CountBaseline) / (Total + TotalBaseline) * (1 - (Count + CountBaseline) / (Total + TotalBaseline)) * (1 / Total + 1 / TotalBaseline),
    AttributableRiskLwr = AttributableRisk - 1.96 * sqrt(ARVar),
    AttributableRiskUpr = AttributableRisk + 1.96 * sqrt(ARVar)
  ) %>%
  dplyr::select(-RRVarBaseline, -RRVar, -ARVar, -CountBaseline, -TotalBaseline, -RateBaselineLwr, -RateBaselineUpr)

MFVacc_DHB_SMpopulation.df <- ERP_MFVacc_SMpopulation.total %>%
  dplyr::left_join(HSU_MFVacc_SMbaseline.total, by = c("DHB", "AgeGroup")) %>%
  dplyr::mutate(
    RelativeRisk    = Rate / RateBaseline,
    RRVar           = ((Total - Count) / Total) / Count,
    RelativeRiskLwr = exp(log(RelativeRisk) - 1.96 * sqrt(RRVar + RRVarBaseline)),
    RelativeRiskUpr = exp(log(RelativeRisk) + 1.96 * sqrt(RRVar + RRVarBaseline)),

    AttributableRisk    = Rate - RateBaseline,
    ARVar               = Variance,
    AttributableRiskLwr = AttributableRisk - 1.96 * sqrt(ARVar + ARVarBaseline),
    AttributableRiskUpr = AttributableRisk + 1.96 * sqrt(ARVar + ARVarBaseline)
  ) %>%
  dplyr::select(-RRVarBaseline, -RRVar, -ARVarBaseline, -ARVar) %>%
  dplyr::bind_rows(ERP_MFVacc_SMpopulation.other)


```

## Rate ratio for Maori males Fully Vaccinated Rates by grouped DHB with 95% CI's
```{r, fig.height= 10, fig.width= 10}


ggplot(subset(MFVacc_DHB_SMpopulation.df, DHB == "Total"), aes(x=factor(AgeGroup, level= level_order), y = RelativeRisk,fill=RelativeRisk))+
  geom_col(fill = "Steel Blue 2")+
  geom_errorbar(aes(min=RelativeRiskLwr, ymax=RelativeRiskUpr), width=0.5) +
  plot_annotation(title = "Maori Males Fully Vaccinated Rate Ratio by Age Group (HSU as baseline)") +
  labs(y= "Rate Ratio",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

```

```{r, eval=FALSE}

#pdf(file="Maori Males Fully Vaccinated Rate Ratio by Age Group (HSU as baseline).pdf", width = 10, height = 10)


ggplot(subset(MFVacc_DHB_SMpopulation.df, DHB == "Total"), aes(x=factor(AgeGroup, level= level_order), y = RelativeRisk,fill=RelativeRisk))+
  geom_col(fill = "Steel Blue 2")+
  geom_errorbar(aes(min=RelativeRiskLwr, ymax=RelativeRiskUpr), width=0.5) +
  plot_annotation(title = "Maori Males Fully Vaccinated Rate Ratio by Age Group (HSU as baseline)") +
  labs(y= "Rate Ratio",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()

```


## code for setting HSU as baseline for Non-Māori Vaccinations

```{r}

HSU_NMFVacc_SMbaseline.total <- HSU_NMFVacc_DHB_SMtot.df
ERP_NMFVacc_SMpopulation.total <- ERP_NMFVacc_DHB_SMtot.df

## Rename variables so we can use them after joining to the other dataset (otherwise we get Rate.x and Rate.y which is a bit confusing).
HSU_NMFVacc_SMbaseline.total <- HSU_NMFVacc_SMbaseline.total %>%
  dplyr::rename(
    RateBaseline     = Rate,
    VarianceBaseline = Variance,
    #W_meanBaseline   = W_mean,
    RateBaselineLwr = Rate_KeyfitzLwr,
    RateBaselineUpr = Rate_KeyfitzUpr
  ) %>%
  dplyr::mutate(
    RRVarBaseline = ((Total - Count) / Total) / Count,
    ARVarBaseline = VarianceBaseline
  ) %>%
  dplyr::select(DHB, AgeGroup, RateBaseline, RRVarBaseline, ARVarBaseline, VarianceBaseline, RateBaselineLwr, RateBaselineUpr)


HSU_NMFVacc_SMbaseline.other <- HSU_NMFVacc_SMnontot.df
ERP_NMFVacc_SMpopulation.other <- ERP_NMFVacc_SMnontot.df



HSU_NMFVacc_SMbaseline.other <- HSU_NMFVacc_SMbaseline.other %>%
  dplyr::mutate(
    RateBaseline = Rate,
    RRVarBaseline = (1 / Count - 1 / Total),
    CountBaseline = Count,
    TotalBaseline = Total,

    RateBaselineLwr = Rate_KeyfitzLwr,
    RateBaselineUpr = Rate_KeyfitzUpr
  ) %>%
  dplyr::select(DHB, AgeGroup, RateBaseline, RRVarBaseline, CountBaseline, TotalBaseline, RateBaselineLwr, RateBaselineUpr)

## Join the baseline and other population datasets, calculating the RR and asssociated CI
ERP_NMFVacc_SMpopulation.other <-ERP_NMFVacc_SMpopulation.other %>%
  dplyr::left_join(HSU_NMFVacc_SMbaseline.other, by = c("DHB", "AgeGroup")) %>%
  dplyr::mutate(
    RelativeRisk = Rate / RateBaseline,
    AttributableRisk = Rate - RateBaseline,
    # RRVar = (1 / Count) * ((Total - Count) / Total),
    RRVar = (1 / Count - 1 / Total),
    RelativeRiskLwr = exp(log(RelativeRisk) - 1.96 * sqrt(RRVar + RRVarBaseline)),
    RelativeRiskUpr = exp(log(RelativeRisk) + 1.96 * sqrt(RRVar + RRVarBaseline)),
    # ARVar = Rate * (1 - Rate) * (1 / Total + 1 / TotalBaseline),
    ARVar = (Count + CountBaseline) / (Total + TotalBaseline) * (1 - (Count + CountBaseline) / (Total + TotalBaseline)) * (1 / Total + 1 / TotalBaseline),
    AttributableRiskLwr = AttributableRisk - 1.96 * sqrt(ARVar),
    AttributableRiskUpr = AttributableRisk + 1.96 * sqrt(ARVar)
  ) %>%
  dplyr::select(-RRVarBaseline, -RRVar, -ARVar, -CountBaseline, -TotalBaseline, -RateBaselineLwr, -RateBaselineUpr)

NMFVacc_DHB_SMpopulation.df <- ERP_NMFVacc_SMpopulation.total %>%
  dplyr::left_join(HSU_NMFVacc_SMbaseline.total, by = c("DHB", "AgeGroup")) %>%
  dplyr::mutate(
    RelativeRisk    = Rate / RateBaseline,
    RRVar           = ((Total - Count) / Total) / Count,
    RelativeRiskLwr = exp(log(RelativeRisk) - 1.96 * sqrt(RRVar + RRVarBaseline)),
    RelativeRiskUpr = exp(log(RelativeRisk) + 1.96 * sqrt(RRVar + RRVarBaseline)),

    AttributableRisk    = Rate - RateBaseline,
    ARVar               = Variance,
    AttributableRiskLwr = AttributableRisk - 1.96 * sqrt(ARVar + ARVarBaseline),
    AttributableRiskUpr = AttributableRisk + 1.96 * sqrt(ARVar + ARVarBaseline)
  ) %>%
  dplyr::select(-RRVarBaseline, -RRVar, -ARVarBaseline, -ARVar) %>%
  dplyr::bind_rows(ERP_NMFVacc_SMpopulation.other)


```

## Rate ratio for Non-Maori males Fully Vaccinated Rates by grouped DHB with 95% CI's
```{r, fig.height= 10, fig.width= 10}


ggplot(subset(NMFVacc_DHB_SMpopulation.df, DHB == "Total"), aes(x=factor(AgeGroup, level= level_order), y = RelativeRisk,fill=RelativeRisk))+
  geom_col(fill = "Steel Blue 2")+
  geom_errorbar(aes(min=RelativeRiskLwr, ymax=RelativeRiskUpr), width=0.5) +
  plot_annotation(title = "Non-Maori Males Fully Vaccinated Rate Ratio by Age Group (HSU as baseline)") +
  labs(y= "Rate Ratio",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

```

```{r, eval=FALSE}

#pdf(file="Non-Maori Males Fully Vaccinated Rate Ratio by Age Group (HSU as baseline).pdf", width = 10, height = 10)


ggplot(subset(NMFVacc_DHB_SMpopulation.df, DHB == "Total"), aes(x=factor(AgeGroup, level= level_order), y = RelativeRisk,fill=RelativeRisk))+
  geom_col(fill = "Steel Blue 2")+
  geom_errorbar(aes(min=RelativeRiskLwr, ymax=RelativeRiskUpr), width=0.5) +
  plot_annotation(title = "Non-Maori Males Fully Vaccinated Rate Ratio by Age Group (HSU as baseline)") +
  labs(y= "Rate Ratio",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()

```




# Total Males fully vaccinated rates by Age (across all DHB)

```{r, fig.height= 10, fig.width= 10}

HSUvsERP_TFVacc_SMnontot.df <- rbind(
  data.frame(HSU_TFVacc_SMnontot.df, population="HSU"),
  data.frame(ERP_TFVacc_SMnontot.df, population="ERP")
)

ggplot(subset(HSUvsERP_TFVacc_SMnontot.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Total Males Fully Vaccinated by Age Group & DHB") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

```

```{r, eval=FALSE}

#pdf(file="Total Males Fully Vaccinated by Age Group & DHB Fullplot.pdf", width = 10, height = 10)

ggplot(subset(HSUvsERP_TFVacc_SMnontot.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Total Males Fully Vaccinated by Age Group & DHB") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()

```

# Non-Maori Males fully vaccinated rates by Age (across all DHB)

```{r, fig.height= 10, fig.width= 10}

HSUvsERP_NMFVacc_SMnontot.df <- rbind(
  data.frame(HSU_NMFVacc_SMnontot.df, population="HSU"),
  data.frame(ERP_NMFVacc_SMnontot.df, population="ERP")
)

ggplot(subset(HSUvsERP_NMFVacc_SMnontot.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Non-Maori Males Fully Vaccinated by Age Group & DHB") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

```

```{r, eval=FALSE}

#pdf(file="Non-Maori Males Fully Vaccinated by Age Group & DHB Fullplot.pdf", width = 10, height = 10)

ggplot(subset(HSUvsERP_NMFVacc_SMnontot.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Non-Maori Males Fully Vaccinated by Age Group & DHB") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()

```


# Maori Males fully vaccinated rates by Age, in depth for each DHB

```{r, fig.height= 10, fig.width= 10}
HSU_MFVacc_nontot_high1.df <- HSU_MFVacc_SMnontot.df[HSU_MFVacc_SMnontot.df$DHB %in% c("Northland", "Waikato","Counties Manukau", "Bay of Plenty"),]
HSU_MFVacc_nontot_high2.df <- HSU_MFVacc_SMnontot.df[HSU_MFVacc_SMnontot.df$DHB %in% c("Waitemata", "Lakes","Tairawhiti", "Hawkes Bay"),]
HSU_MFVacc_nontot_mid1.df <- HSU_MFVacc_SMnontot.df[HSU_MFVacc_SMnontot.df$DHB %in% c("Canterbury", "Southern", "Capital and Coast", "Auckland"),]
HSU_MFVacc_nontot_mid2.df <- HSU_MFVacc_SMnontot.df[HSU_MFVacc_SMnontot.df$DHB %in% c("MidCentral", "Hutt Valley", "Taranaki", "Whanganui"),]

HSU_MFVacc_nontot_low.df <- HSU_MFVacc_SMnontot.df[HSU_MFVacc_SMnontot.df$DHB %in% c("South Canterbury", "West Coast", "Nelson Marlborough", "Wairarapa"),]


ERP_MFVacc_nontot_high1.df <- ERP_MFVacc_SMnontot.df[ERP_MFVacc_SMnontot.df$DHB %in% c("Northland", "Waikato","Counties Manukau", "Bay of Plenty"),]
ERP_MFVacc_nontot_high2.df <- ERP_MFVacc_SMnontot.df[ERP_MFVacc_SMnontot.df$DHB %in% c("Waitemata", "Lakes","Tairawhiti", "Hawkes Bay"),]
ERP_MFVacc_nontot_mid1.df <- ERP_MFVacc_SMnontot.df[ERP_MFVacc_SMnontot.df$DHB %in% c("Canterbury", "Southern", "Capital and Coast", "Auckland"),]

ERP_MFVacc_nontot_mid2.df <- ERP_MFVacc_SMnontot.df[ERP_MFVacc_SMnontot.df$DHB %in% c("MidCentral", "Hutt Valley", "Taranaki", "Whanganui"),]
ERP_MFVacc_nontot_low.df <- ERP_MFVacc_SMnontot.df[ERP_MFVacc_SMnontot.df$DHB %in% c("South Canterbury", "West Coast", "Nelson Marlborough", "Wairarapa"),]



HSUvsERP_MFVacc_nontot_high1.df <- rbind(
  data.frame(HSU_MFVacc_nontot_high1.df, population="HSU"),
  data.frame(ERP_MFVacc_nontot_high1.df, population="ERP")
)

ggplot(subset(HSUvsERP_MFVacc_nontot_high1.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group & DHB") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}

#pdf(file="Maori Males Fully Vaccinated by Age Group & DHB high1.pdf", width = 10, height = 10)


ggplot(subset(HSUvsERP_MFVacc_nontot_high1.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group & DHB") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()

```

```{r}

HSUvsERP_MFVacc_nontot_high2.df <- rbind(
  data.frame(HSU_MFVacc_nontot_high2.df, population="HSU"),
  data.frame(ERP_MFVacc_nontot_high2.df, population="ERP")
)

ggplot(subset(HSUvsERP_MFVacc_nontot_high2.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group & DHB") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))
```


```{r, eval=FALSE}

#pdf(file="Maori Males Fully Vaccinated by Age Group & DHB high2.pdf", width = 10, height = 10)


ggplot(subset(HSUvsERP_MFVacc_nontot_high2.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group & DHB") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```


```{r}
HSUvsERP_MFVacc_nontot_mid1.df <- rbind(
  data.frame(HSU_MFVacc_nontot_mid1.df, population="HSU"),
  data.frame(ERP_MFVacc_nontot_mid1.df, population="ERP")
)

ggplot(subset(HSUvsERP_MFVacc_nontot_mid1.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group & DHB") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}


#pdf(file="Maori Males Fully Vaccinated by Age Group & DHB mid1.pdf", width = 10, height = 10)


ggplot(subset(HSUvsERP_MFVacc_nontot_mid1.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group & DHB") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```

```{r}
HSUvsERP_MFVacc_nontot_mid2.df <- rbind(
  data.frame(HSU_MFVacc_nontot_mid2.df, population="HSU"),
  data.frame(ERP_MFVacc_nontot_mid2.df, population="ERP")
)

ggplot(subset(HSUvsERP_MFVacc_nontot_mid2.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group & DHB") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}

#pdf(file="Maori Males Fully Vaccinated by Age Group & DHB mid2.pdf", width = 10, height = 10)


ggplot(subset(HSUvsERP_MFVacc_nontot_mid2.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group & DHB") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```

```{r}
HSUvsERP_MFVacc_nontot_low.df <- rbind(
  data.frame(HSU_MFVacc_nontot_low.df, population="HSU"),
  data.frame(ERP_MFVacc_nontot_low.df, population="ERP")
)

ggplot(subset(HSUvsERP_MFVacc_nontot_low.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group & DHB") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}
#pdf(file="Maori Males Fully Vaccinated by Age Group & DHB low.pdf", width = 10, height = 10)

ggplot(subset(HSUvsERP_MFVacc_nontot_low.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group & DHB") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()


```

## presenting lowest vs. highest
```{r, fig.height= 10, fig.width= 10}
# separated by rate levels

HSU_MFVacc_nontot_highest.df <- HSU_MFVacc_SMnontot.df[HSU_MFVacc_SMnontot.df$DHB %in% c("Northland"),]
HSU_MFVacc_nontot_lowest.df <- HSU_MFVacc_SMnontot.df[HSU_MFVacc_SMnontot.df$DHB %in% c("West Coast"),]

ERP_MFVacc_nontot_highest.df <- ERP_MFVacc_SMnontot.df[ERP_MFVacc_SMnontot.df$DHB %in% c("Northland"),]
ERP_MFVacc_nontot_lowest.df <- ERP_MFVacc_SMnontot.df[ERP_MFVacc_SMnontot.df$DHB %in% c("West Coast"),]



HSUvsERP_MFVacc_low.df <- rbind(
  data.frame(HSU_MFVacc_nontot_lowest.df, population="HSU"),
  data.frame(ERP_MFVacc_nontot_lowest.df, population="ERP")
)

ggplot(subset(HSUvsERP_MFVacc_low.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group for West Coast DHB (Lowest Rates per 100,000)") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}

#pdf(file="Maori Males Fully Vaccinated by Age Group & lowest DHB.pdf", width = 10, height = 10)

ggplot(subset(HSUvsERP_MFVacc_low.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group for West Coast DHB (Lowest Rates per 100,000)") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```

```{r}
HSUvsERP_MFVacc_high.df <- rbind(
  data.frame(HSU_MFVacc_nontot_highest.df, population="HSU"),
  data.frame(ERP_MFVacc_nontot_highest.df, population="ERP")
)

ggplot(subset(HSUvsERP_MFVacc_high.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group for Northland DHB (Highest Rates per 100,000)") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}
#pdf(file="Maori Males Fully Vaccinated by Age Group & highest DHB.pdf", width = 10, height = 10)

ggplot(subset(HSUvsERP_MFVacc_high.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group for Northland DHB (Highest Rates per 100,000)") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()
```

```{r}
## collating plot into one for differences

HSU_MFVacc_nontot_lowvshigh.df <- HSU_MFVacc_SMnontot.df[HSU_MFVacc_SMnontot.df$DHB %in% c("Northland","West Coast"),]
ERP_MFVacc_nontot_lowvshigh.df <- ERP_MFVacc_SMnontot.df[ERP_MFVacc_SMnontot.df$DHB %in% c("Northland","West Coast"),]


HSUvsERP_MFVacc_lowvshigh.df <- rbind(
  data.frame(HSU_MFVacc_nontot_lowvshigh.df, population="HSU"),
  data.frame(ERP_MFVacc_nontot_lowvshigh.df, population="ERP")
)

ggplot(subset(HSUvsERP_MFVacc_lowvshigh.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group & DHB (Lowest vs. Highest rates per 100,000)") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval=FALSE}

#pdf(file="Maori Males Fully Vaccinated by Age Group & highest vs. lowest DHB.pdf", width = 10, height = 10)

ggplot(subset(HSUvsERP_MFVacc_lowvshigh.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group & DHB (Lowest vs. Highest rates per 100,000)") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()

```

## presenting highest diff in comparison to Māori females
```{r, fig.height= 10, fig.width= 10}
# separated by rate levels

HSU_MFVacc_nontot_highestdiff.df <- HSU_MFVacc_SMnontot.df[HSU_MFVacc_SMnontot.df$DHB %in% c("Counties Manukau"),]

ERP_MFVacc_nontot_highestdiff.df <- ERP_MFVacc_SMnontot.df[ERP_MFVacc_SMnontot.df$DHB %in% c("Counties Manukau"),]


HSUvsERP_MFVacc_highestdiff.df <- rbind(
  data.frame(HSU_MFVacc_nontot_highestdiff.df, population="HSU"),
  data.frame(ERP_MFVacc_nontot_highestdiff.df, population="ERP")
)

ggplot(subset(HSUvsERP_MFVacc_highestdiff.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group for Counties Manukau DHB (Rates per 100,000)") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

```

```{r, eval=FALSE}
#pdf(file="Maori Males Fully Vaccinated by Age Group & highest diff DHB.pdf", width = 10, height = 10)

ggplot(subset(HSUvsERP_MFVacc_highestdiff.df), aes(x=factor(AgeGroup, level= level_order), y = RateMult, fill = population, group=population)) +
  geom_col(position = position_dodge()) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5,hjust=1)) +
  geom_errorbar(aes(ymin=Rate_Gamma1Lwr, ymax=Rate_Gamma1Upr), position = position_dodge(width = 0.85), width = 0.5) +
  facet_wrap(~DHB) +
  plot_annotation(title = "Maori Males Fully Vaccinated by Age Group for Counties Manukau DHB (Rates per 100,000)") +
  labs(y= "Rate per 100,000",
       x= "Age Groups") &
  theme(plot.title = element_text(hjust = 0.5))

dev.off()


```

